Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-22 paper/paper.Rmd
fix bug caused by changes to metadata code

# Models per forecast date
models_per_forecast <- metadata |>
  summarise_forecasts_by(by = "target_end_date")

@@

locs_per_model_single_date <- metadata |>
    summarise_forecasts_by(
      var = "location", by = c("model", "target_end_date")
    ) |>
    DT(, unique(.SD[n == max(n), .(n)]), by = "model")

locs_per_model_date <- metadata |>
  summarise_forecasts_by(
    var = "location", by = c("model", "target_end_date")
  ) |>
  DT(locs_per_model_single_date[, .(model, max_n = n)], on = "model") |>
  DT(, n_per := n / max_n) |>
  DT(, .SD[!all(n == max_n)], by = "model")

models_per_loc_date <- metadata |>
  summarise_forecasts_by(var = "model", by = c("target_end_date", "location"))

>>>>

# Models per forecast date
models_per_forecast <- metadata |>
  summarise_forecasts_by(by = "forecast_date")

@@

locs_per_model_single_date <- metadata |>
    summarise_forecasts_by(
      var = "location", by = c("model", "forecast_date")
    ) |>
    DT(, unique(.SD[n == max(n), .(n)]), by = "model")

locs_per_model_date <- metadata |>
  summarise_forecasts_by(
    var = "location", by = c("model", "forecast_date")
  ) |>
  DT(locs_per_model_single_date[, .(model, max_n = n)], on = "model") |>
  DT(, n_per := n / max_n) |>
  DT(, .SD[!all(n == max_n)], by = "model")

models_per_loc_date <- metadata |>
  summarise_forecasts_by(var = "model", by = c("forecast_date", "location"))
